% !TEX root = main.tex
\section{Extended Nebulas Rank}
Core Nebulas Rank is used to evaluate an individual account’s contribution to the economy aggregate. It’s vital for Core Nebulas Rank to the use cases of both Proof of Devotion (PoD) and Developer Incentive Plan (DIP), and the Core Nebulas Rank actually matches with their use cases. However, as we also noticed, there are some other use cases that they may require a different evaluation, and for these, we designed Extended Nebulas Rank. Extended Nebulas Rank is based on the Core Nebulas Rank, to guarantee continuous incentive to the entire Nebulas economy even under different use cases.

\subsection{Smart Contract Oriented Extended Nebulas Rank}
The rank of smart contract plays an important role within the economy. On one hand, it helps user find high quality DApps. And on the other hand, it will also motivate the developers to build high quality Dapps, so the economy can continuously expand and stably.

Ranking of smart contract depends on two factors: the call from users account address to the smart contract, and the calls between different smart contracts. The call from user account address to smart contracts reflects the truth that the users account address is actually distributing its contribution to the aggregate economy of all smart contracts, since each smart contract has its own initial NR. The calls between smart contracts can also be treated as a directed acyclic graph. Therefore, we utilise Page Rank algorithm to calculate NR for each smart contract.



\subsection{Multi-dimension Extended Nebulas Rank}
We also found out that some applications require multi-dimensional data in order to compute the correlation between different kinds of data on chain. For example, in a blockchain based advertisement system, we need to get the correlation between the advertisement and the user from different dimensions. In this situation, we use Extended Nebulas Rank as it is multi-dimensional, can be represented as a vector, we also use Core Nebulas Rank as one of the dimensions.

Extended Nebulas Rank is multi-dimensional, and with the exception of Core Nebulas Rank, the other dimensions all depend on concrete applications. How to implement those dimensions also depends on the application itself. Nevertheless, the calculation algorithms can always reference the calculations of the Core Nebulas Rank algorithm.

\vspace{2em}

Starting from a real use case, we design the Extended Nebulas Rank for smart contracts, and have described an implementation method of Extended Nebulas Rank. We also illustrated the corresponding evaluation mechanism of this algorithm, and proposed the multi-dimensional Extended Nebulas Rank, which shows the possibility for our evaluation mechanism to be used in other use-cases.
